---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis Build Status](https://travis-ci.org/stufield/grapevine.svg?branch=master)](https://travis-ci.org/stufield/grapevine)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/stufield/grapevine?branch=master&svg=true)](https://ci.appveyor.com/project/stufield/grapevine)
[![CRAN_Status](http://www.r-pkg.org/badges/version/grapevine)](https://cran.r-project.org/package=grapevine)
[![codecov](https://codecov.io/gh/stufield/grapevine/branch/master/graph/badge.svg)](https://codecov.io/gh/stufield/grapevine)



# The `grapevine` package

Commonly referred to as "binary operators", functions that have a left and
right side are typically defined using `%%` symbols. Thus the colloquial
term "grapevine". The functions below represent a growing list of useful
binary operators that come in handy when working in an R environment.



## Installation

To install the latest `development` version of `grapevine` from **GitHub**,
first install the [devtools](https://CRAN.R-project.org/package=devtools)
package and run:

```{r, eval = FALSE}
devtools::install_github("stufield/grapevine", build = TRUE)
```

If you specify a tag, you can install a GitHub release.

```{r, eval = FALSE}
devtools::install_github("stufield/grapevine@v0.0.1", build = TRUE)
```


## LICENSE

This package (suite of programs) is free software; you can redistribute 
it and/or modify it under the terms of the MIT License.
See please see the [LICENSE](LICENSE).
By using in this package you agree to abide by its terms.


-------------


Created by [Rmarkdown](https://github.com/rstudio/rmarkdown)
(v`r utils::packageVersion("rmarkdown")`) and `r R.version$version.string`. 
