---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r setup, include = FALSE}
options(width = 100)
Sys.setlocale("LC_COLLATE", "en_US.UTF-8") # ensure common sorting envir
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
ver <- desc::desc_get_version(".")
ver <- paste0("https://img.shields.io/badge/Version-", ver,
              "-success.svg?style=flat&logo=github")
```

<!-- badges: start -->
![GitHub version](`r ver`)
[![CRAN status](http://www.r-pkg.org/badges/version/helpr)](https://cran.r-project.org/package=helpr)
[![R-CMD-check](https://github.com/stufield/helpr/workflows/R-CMD-check/badge.svg)](https://github.com/stufield/helpr/actions)
[![](https://cranlogs.r-pkg.org/badges/grand-total/helpr)](https://cran.r-project.org/package=helpr)
[![Codecov test coverage](https://codecov.io/gh/stufield/helpr/branch/main/graph/badge.svg)](https://app.codecov.io/gh/stufield/helpr?branch=main)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://choosealicense.com/licenses/mit/)
<!-- badges: end -->



# The `grapevine` package

Commonly referred to as "binary operators", functions that have a left and
right side are typically defined using `%%` symbols. Thus the colloquial term
"grapevine". The functions below represent a growing list of useful binary
operators that come in handy when working in an R environment.



## Installation

To install the latest `development` version of `grapevine` from **GitHub**,
first install the [devtools](https://CRAN.R-project.org/package=devtools)
package and run:

```{r install-github, eval = FALSE}
# current dev version
remotes::install_github("stufield/grapevine")

# or a specific version
remotes::install_github("stufield/grapevine@v0.0.1")
```


## Functions

- `%||%`
- `%@@%`
- `%@@%<-`
- `%==%`
- `%!=%`
- `%===%`
- `%set%`
- `%!set%`
- `%[[%`
- `%null%`
- `%!in%`


